Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-05-06 paper/paper.Rmd
rough draft paragraph on object architecture/interfaces, issue #126

etc

@@

@@

>>>>

- add a paragraph with more information on spCV using spatial partitionings

@@

- add a paragraph on spatiotemporal partitioning

@@

- *add one/two paragraphs outlining mlr3's object model and mlr3psatiotempcv's place within. someting along the lines of:*

Within \pkg{mlr}, partitioning strategies are represented by resampling objects (correct?) of class xyz, which are generated within mlr3 itself (for regular random CV, correct??) or within specialized extensions such as mlr3spatiotempcv.
In the ML pipeline, these objects are used for model assessment by ... objects/tasks/whatever and for model selection by ... objects/tasks/..., providing a consistent framework for both tasks that is necessary to optimize learners for a given prediction problem [@schratz2019].

Resampling objects in mlr3spatiotmpcv inherit from and can be created from established object classes for geospatial data in R, including simple features (add a general reference, maybe Lovelace), which facilitates its integration into domain-specific workflows in the geospatial sciences. This includes support for geographic coordinate reference systems and their respective distance measures in projected planar space or on the unprojected ellipsoid (corrrect?). Of course, non-spatial data tables with coordinates as variables are also supported.
